%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref}


\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Sharelatex Example},
    bookmarks=true,
    pdfpagemode=FullScreen,
}


\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Tess Lallemant} % Your name
\address{434 Warren Hall, Cornell University, Ithaca, NY 14850} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{tl796@cornell.edu \\ tess.lallemant@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Cornell University, NY} \hfill {\em 2020 - Present} 
\\ PhD Student - Dyson School of Applied Economics and Management \\
Advised by: Dr. Brian Dillon \\
\\{\bf University of Illinois at Urbana Champaign, IL} \hfill {\em 2018 - 2020} 
\\ Master's of Science in Agricultural and Applied Economics\\
Advised by: Dr. Kathy Baylis\\
\\{\bf Reed College, OR} \hfill {\em 2010 - 2014} 
\\ Bachelors in Political Science
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

\begin{rSubsection}{Cornell University}{}{Research Assistant - Dr. Joanna Upton}{Fall 2022 - Present}
\item Processed data for Madagascar as part of Monthly Interval Resilience Analysis (MIRA)
\item Coordinated and conducted qualitative data collection through focus groups (in field)
\end{rSubsection}

\begin{rSubsection}{University of Illinois at Urbana Champaign}{}{Research Assistant - Dr. Hope Michelson}{Spring 2019 - Present}
\item Analysed of high frequency geospatial data at household level using R and ArcGIS
\vskip 0.02in
\textit{Research Assistant - Dr. Madhu Khanna}\hfill \textit{Summer 2019 - Fall 2019}
\item Consolidated literature for costs/benefits of ecosystem services of the Araguaia River Corridor, Brazil
\vskip 0.02in
\textit{Research Assistant - Dr. Kathy Baylis}\hfill \textit{Summer 2019}
\item Processed and analyzed of remote sensing data to calibrate crop/geographic specific shocks.
\end{rSubsection}

\begin{rSubsection}{International Food Policy Research Institute (IFPRI)}{\textit{May 2015 - August 2018}}{Research Analyst (2018), Research Assistant (2015-2018)}{}
\item Assisted in modeling, coding, and simulations of economic models using R, SQL, MySQL, and GAMS
\item Led and managed the updated database for agricultural price distortion data (\href{http://ag-incentives.org/}{Ag-Incentives})
\item Designed, programmed and analyzed surveys for projects (Delphi approach)
\end{rSubsection}

\begin{rSubsection}{World Bank Group - DEC}{\textit{2014 - 2015}}{Consultant}{}
\item Processed household survey data for tens of countries using SQL
\item Conducted research regarding food consumption and poverty using SQL and R
\end{rSubsection}

\begin{rSubsection}{International Association of Agricultural Economists (IAAE)}{\textit{2014 - 2015}}{Program Coordinator - International Conference of Agricultural Economists (ICAE) 2015}{}
\item Coordinated conference program, logistics and submission review process
\end{rSubsection}

\end{rSection}

\newpage
\begin{rSection}{Teaching Experience} 
\begin{rSubsection}{Cornell University}{}{Teaching Assistant}{}
\item Leadership and Management in Sports (AEM 3320) \hfill \textit{Fall 2021}
\item Better Decisions for Life, Love and Money (AEM 2020/PSYCH 2940) \hfill \textit{Spring 2022}
\item Behavioral Economics and Managerial Decisions (AEM 4140) \hfill \textit{Spring 2023}
\end{rSubsection}

\begin{rSubsection}{University of Illinois at Urbana Champaign}{}{Teaching Assistant}{}
\item Agricultural and Food Policies (ACE 456) \hfill \textit{Spring 2019}
\item Environmental Law (ACE 406) \hfill \textit{Fall 2018}
\item Food Law (ACE 306) \hfill \textit{Fall 2018}
\end{rSubsection}
\end{rSection}
%--------------------------------------------------------------------------------
%    Projects
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Theses}
{\bf Master's Thesis } 
{Thesis Advisor: Dr. Kathy Baylis}
\\Using a novel data set of monthly price data from over 900 geocoded markets in Africa, Latin America and Asia, I link remotely-sensed weather data by local cropped area and season, and study how trade-openness can mitigate or exacerbate the effects of climate shocks on the price of primary staple crops. \\
\\ {\bf Undergraduate Thesis } {Thesis Advisor: Dr. Mariela Szwarcberg}\\
Thailand and the Politics of Hope - An investigation of the 2013-2014 political crisis in Thailand through an analysis of the use of corruption, populism and patronage.

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages \ & English (Fluent), French (Native), Thai (Fluent), Spanish (Intermediate)\\
Modeling and Analysis \ & R, Stata, ArcGIS, SQL, GAMS (Working Knowledge)\\
Software \& Tools & MS Office, LaTeX, R-Markdown \\
Project Management & Slack, Assembla, Basecamp \\
\end{tabular}

\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards} 

\begin{rSubsection}{University of Illinois at Urbana Champaign}{\textit{2020}}{Award for Outstanding Master's Student}{}
\end{rSubsection}

\begin{rSubsection}{University of Illinois at Urbana Champaign}{\textit{2018}}{Ranked Excellent as Teacher's Assistant - Food Law (Fall 2018)}{}
\end{rSubsection} 

\begin{rSubsection}{International Food Policy Research Institute (IFPRI)}{\textit{2016}}{Merit based reward for outstanding accomplishments as recommended by the Division Director}{}
\end{rSubsection}
\begin{rSubsection}{Reed College}{\textit{2014}}{Commendation for Academic Excellence (2013-2014 Academic Year)}{}
\end{rSubsection}
\end{rSection}

%	EXAMPLE SECTION
%---------------------------------------------------------------------------------------
\begin{rSection}{Service}

\begin{rSubsection}{Cornell University}{}{}{}
\item Co-Editor in Chief of \href{https://www.econthatmatters.com/}{Economics That Really Matters} blog \hfill \textit{2023-}
\item Co-Social Chair of the Graduate Student Association \hfill \textit{2022-2023}

\end{rSubsection}

\begin{rSubsection}{University of Illinois at Urbana Champaign}{}{}{}
\item Vice President of the Graduate Student Organization \hfill \textit{2019-2020}
\end{rSubsection}

\end{rSection}

\newpage
\begin{rSection}{Reports, Briefs, Publications} 
{\bf Publications, Reports and Working Papers}
\item Laborde, \textbf{T. Lallemant}, K. McDougal, C. Smaller, F. Traore. 2018. “Transforming Agriculture in Africa & Asia" Waht are the policy priorities” Winnipeg,
Manitoba, Canada: International Institute for Sustainable Development (IISD).
 \href{https://www.iisd.org/library/transforming-agriculture-africa-asia-what-are-policy-priorities} {Link}
\item Tokgoz, S., C. Marciniak, F. Majeed, \textbf{T. Lallemant}. “Chapter 9: Processing of Individual Data Sources.” In Laborde, David, ed.; and Tokgoz, Simla, ed. 2018. Ag-Incentives Documentation. ag-incentives.org.
(Forthcoming)
\item \textbf{Lallemant, T.}, D. Laborde, C. Marciniak, S. Tokgoz. “Chapter 10: The consolidated database.” in Laborde,
David, ed.; and Tokgoz, Simla, ed. 2018. Ag-Incentives Documentation. ag-incentives.org. (Forthcoming)
\item Laborde, D., \textbf{T. Lallemant}. 2017. “Agricultural Price incentives: Towards Gender-differentiated Indicators”
International Food Policy Research Institute (IFPRI), Washington, D.C.
\item Laborde, D., W. Martin, S. Tokgoz, \textbf{T. Lallemant}, F. Majeed. 2017. “Poverty impacts of widely adopted
CGIAR innovations.” IFPRI Report. International Food Policy Research Institute (IFPRI), Washington, D.C.,
Soon Available Online
\item Laborde, D., L. Bizikova, \textbf{T. Lallemant}, C. Smaller. 2016. “Ending hunger: What would it cost?” Winnipeg,
Manitoba, Canada: International Institute for Sustainable Development (IISD).
 \href{http://www.iisd.org/sites/default/files/publications/ending-hunger-what-would-it-cost.pdf} {Link}
\item Laborde, D., L. Bizikova, \textbf{T. Lallemant}, C. Smaller. 2016. “What Is the Link Between Hunger and Migration?”
Winnipeg, Manitoba, Canada: International Institute for Sustainable Development (IISD).
 \href{http://www.iisd.org/library/what-link-between-hunger-and-migration} {Link}
\item Laborde, D., \textbf{T. Lallemant}. 2016. “Technical Appendix - What Is the Link Between Hunger and Migration?”
Winnipeg, Manitoba, Canada: International Institute for Sustainable Development (IISD).
 \href{https://www.iisd.org/sites/default/files/uploads/link-between-hunger-migration-technical-appendix.pdf} {Link}
\vskip 0.02in
{\bf Conference and Workshop Presentations}
\item Baylis, K., \textbf{T. Lallemant}. 2019. “Do trade policies mitigate the effects of climate shocks on maize prices?”. Presented at International Agricultural Trade Research Consortium (IATRC 2019),Washington D.C, December 8 - 10,2019

\item Laborde, D., L. Bizikova, \textbf{T. Lallemant}, C. Smaller. 2016. “Ending hunger: What would it cost?” Winnipeg,
Manitoba, Canada: International Institute for Sustainable Development (IISD). Presented at ICABR 2018,
Disruptive Innovations, Value Chains, and Rural Development. World Bank, Washington D.C, June 12-15,
2018
 \href{http://www.worldbank.org/en/events/2017/10/11/disruptive-innovations-value-chains-and-ruraldevelopment} {Link}
\item Laborde, D., \textbf{T. Lallemant}. 2017. “Agricultural Price incentives: Towards Gender-differentiated Indicators”.
International Food Policy Research Institute (IFPRI), Washington, D.C. Presented at CGIAR Annual Scientific
Conference and Capacity Development Workshop in Amsterdam, Netherlands, December 5-8, 2017
 \href{http://gender.cgiar.org/call-papers-cgiar-collaborative-platform-gender-research-scientific-conferencedecember-
5-6-2017} {Link}
\vskip 0.02in
{\bf Other Media}
\item Laborde, D., \textbf{T. Lallemant}. International Food Policy Research Institute (IFPRI), Washington, D.C. “Ending
Hunger: What Would It Cost?” YouTube, 19 Dec. 2017,
 \href{www.youtube.com/watch?v=l9N8Wwm4yIc&feature=youtu.be}{Link}
\item Bizikova, L., C. Smaller, D. Laborde, \textbf{T. Lallemant}. “Can We End Hunger By 2030?” HuffPost Canada,
HuffPost, 24 Oct. 2016, 
 \href{www.huffingtonpost.ca/development-unplugged/can-we-end-hunger-by-2030_b_12588908.html}{Link}


\end{rSection}

\end{document}
